Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-19 forecast/paper/paper.tex
Temp commit so I can merge

% Please add a significance statement to explain the relevance of your work
\significancestatement{Forecasting is a critical element of the public health
  response to any fast-moving epidemic or pandemic.  Predicting the future
  spread of some disease process, based on disease activity in the recent
  past---say, using what is known as autoregressive modeling in the time series
  literature---is a basic and widely-used method.  In this paper we study
  whether including auxiliary indicators as additional features in such an
  autoregressive model can be useful in COVID-19 case forecasting and hotspot
  prediction.  We find that indicators based on de-identified medical insurance 
  claims, self-reported symptoms through online surveys, and COVID-related
  internet% Capitalization is apparently
  % in question: https://en.wikipedia.org/wiki/Capitalization_of_Internet
  search activity all provide a nontrivial boost in accuracy, though
  their utility generally depends the pandemic's local dynamics (upswing,
  downswing, or flat period) at prediction time.
}

  % TODO % For reference, below is the indicators paper one.
  % To study the COVID-19 pandemic, its effects on society,
  % and measures for reducing its spread, researchers need detailed data on the
  % course of the pandemic. Standard public health data streams suffer
  % inconsistent reporting and frequent, unexpected revisions. They also miss
  % other aspects of a population's behavior, worthy of consideration. We
  % present an open database of COVID signals in the United States, measured at
  % the county level and updated daily. These include traditionally reported
  % COVID cases and deaths, and many others: signals based on measures of
  % mobility, social distancing, internet search trends, self-reported symptoms,
  % and patterns COVID-related activity in de-identified medical insurance 
  % claims. The database provides all signals in a common, easy-to-use format,
  % empowering both  public health research and operational decision-making. 
%}

>>>>

% Please add a significance statement to explain the relevance of your work
\significancestatement{Forecasting is a critical element of the public health
  response to any fast-moving epidemic or pandemic.  Predicting the future
  spread of some disease process, based on disease activity in the recent
  past---say, using what is known as autoregressive modeling in the time series
  literature---is a basic and widely-used method.  In this paper we study
  whether including auxiliary indicators as additional features in such an
  autoregressive model can be useful in COVID-19 case forecasting and hotspot
  prediction.  We find that indicators based on de-identified medical insurance 
  claims, self-reported symptoms through online surveys, and COVID-related
  internet search activity all provide a nontrivial boost in accuracy, though
  their utility generally depends the pandemic's local dynamics (upswing,
  downswing, or flat period) at prediction time.
}
